The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201911/CIV_CLQs_20191105v1.tex
CIV tex/ tidy up

\author[Bercow]
{%The RH John~S.~Bercow, MP, {\it et al.} 
Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor and Daniel Stern$^{6}$ 
\\
% List of institutions
%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has been recently re-invigorated the
field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

@@

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}, with one dominating over the other depending on the shape
of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.

The Sloan Digital Sky Survey Reverberation Mapping Project
\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
\civ. Noting the biases associated with \civ Emission Line Properties
\citep[e.g. increasing systematic offsets with decreasing
signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
significant time delays between the continuum and the CIV 1549
emission line in 52 quasars, and investigate the \civ
radius-luminosity relationship.

\civ\ is also known to exhibit significant displacements to the
blue and these `blueshifts' almost certainly signal the presence of
strong outflows. As a consequence, single-epoch virial black hole (BH)
mass estimates derived from \civ\ velocity widths are known to be
systematically biased compared to masses from the hydrogen Balmer
lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
($L$Bol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
both \civ\ and Balmer line spectra, we have quantified the bias in \civ
BH masses as a function of the \civ\ blueshift. \civ\ BH masses are
shown to be a factor of 5 larger than the corresponding Balmer-line
masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
by almost an order of magnitude at the most extreme blueshifts,
$\gtrsim$5000 km s$^{-1}$.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

@@

\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
software package which among other quantities provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
and setting $E(B-V)=0.00$.

\citet{Hamann2017} investigate in robust detail the UV continuum and
the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
adjacent continuum are covered by BOSS. These measurements provide
line profile information and flux ratios\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
their \civ properties in order to understand the high-$z$ ``Extremely
Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
Zakamska2019}.  As such, these measurements can be taken as the `gold
standard' for \civ line measurement, though this is only for two out of
our nine spectra.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Emission line evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

The Balmer series in hydrogen is due to the recombination cascade
between different principal quantum numbers $n$, and
the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
%%
Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
%%
\civ\ is one of the strongest collisionally excited lines in quasar
spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
canonical BELR parameters deduced over from early analysis of the
\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
H$^{+}$).

@@

@@

 \label{tab:LineMeasurement}

@@

%%
%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
%%
%% Using    C IV

@@

                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\

@@

                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
 J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\

@@

                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\

@@

@@

  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.

@@

        Kol17 is \citet{Kozlowski2017}.
        Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.}

@@

\subsection{The \civ\ Baldwin Effect}
The Baldwin Effect (Baldwin 1977) is an empirical %inverse
relation between emission-line REWs and continuum luminosity in
quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}
%%
There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
so that as the underlying UV continuum luminosity increases, the EW decreses,
see Figure~\ref{fig:CIV_Baldwin}
The slope $\beta$ is $-0.1997$. 
Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
in line with that from \citet{Hamann2017} ($\beta=-0.23$.

@@

%{\bf Our Eddington ratios \\
%Done 1\% \\
%Coatman, Hewett say \civ\ masses are okay.\\
%But what are these Eddington ratios? \\
%Low state BHs vs. High-mass BHs... \\
%Coatman et al?? Blue-shiftted \\ }
\section{Discussion}
\civ\ probes the photoionization environment produced by the innermost
disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
thin disk models, large changes in the continuum flux are not
permitted over short timescales due to the relatively long viscous
time associated with such disks. Given the observed short timescale
continuum variations, it is not surprising that the \citet{SS73} disk may fail
on other fronts. The \civ\ variations observed in our sources... 
%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\subsection{Eddington ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

The soft X-ray excess – the excess of X-rays below 2 keV with respect
to the extrapo- lation of the hard X-ray spectral continuum model – is
a very common feature among type 1 active galactic nuclei (AGN). 
\citet{NodaDone2018} note that
The soft X-ray excess produces most of the ionizing photons, so its
dramatic drop leads to the disappearance of the broad-line region,
driving the ``changing-look'' phenomena.  major difference is that
radiation pressure should be much more important in AGNs, so that the
sound speed is much faster than expected from the gas temperature.
%%
This spectral hardening appears similar to the soft-to-hard state
transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
an advection dominated accretion flow, while the overall drop in
luminosity appears consistent with the hydrogen ionization disc
instability.  Crucially \citet{NodaDone2018} make the prediction that
all changing-look AGNs are similarly associated with the state
transition at $L / L_{\rm Edd} \sim$a few per cent.
%%
\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
\citet{JiangYF2019arXiv} use global three dimensional radiation
magneto-hydrodynamic simulations to study the properties of inner
regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
black hole with mass accretion rates reaching 7\% and 20\% of the
Eddington value.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}

\subsection{Variability around billion solar mass black holes} 
The Event Horizon Telescope (EHT) mapped the central compact radio
source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI, EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV, EHT2019_PaperVI} .

>>>>

\author[Ross {\it et al.}]
{%The RH John~S.~Bercow, MP, {\it et al.} 
Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor and Daniel Stern$^{6}$ 
\\
% List of institutions
%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a 10$^{7}$ M$_{\odot}$ central supermassive black hole
(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has been recently re-invigorated the
field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

@@

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
SDSS quasars, concentrating on the properties of the \civ\ emission
line. These authors consider two well-known effects involving the
\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
with respect to the systemic redshift. \citet{Richards2011} conclude
that these two \civ\ parameters (EQW and blueshift) are capturing an
important trade-off between ``disk'' and ``wind'' components in the
disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
Elvis2000, Proga2000}, with one dominating over the other depending on
the shape of the SED \citep[][strong \civ\ EQW indicates a more
ionizing SED and large \civ\ blueshift indicating a less ionizing SED
]{Leighly2004b}.

The Sloan Digital Sky Survey Reverberation Mapping Project
\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
\civ. Noting the biases associated with \civ\ emission line properties
\citep[such as increasing systematic offsets with decreasing
signal-to-noise; ][]{Denney2016}, \citet{Grier2019} report report
significant time delays between the continuum and the CIV 1549
emission line in 52 quasars, and investigate the \civ\ 
radius-luminosity relationship.

\civ\ is also known to exhibit significant displacements to the blue
and these `blueshifts' almost certainly signal the presence of strong
outflows. As a consequence, single-epoch virial black hole (BH) mass
estimates derived from \civ\ velocity widths are known to be
systematically biased compared to masses from the hydrogen Balmer
lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
($L_{\rm Bol} = 10^{45.5 - 48}$ erg s$^{-1}$), redshift $1.5 < z <
4.0$ quasars with both \civ\ and Balmer line spectra, we have
quantified the bias in \civ BH masses as a function of the \civ\
blueshift. \civ\ BH masses are shown to be a factor of 5 larger than
the corresponding Balmer-line masses at C IV blueshifts of 3000 km
s$^{-1}1$ and are overestimated by almost an order of magnitude at the
most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ EWs, and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

@@

\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
software package which among other quantities provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
and setting $E(B-V)=0.00$.
%%
The host galaxy and blended iron emission at rest-frame optical wavelengths components
are automatically disabled when they can not be constrained by the available data,
such as the case for all our objects (we do not have infrared spectral data).
%%

\citet{Hamann2017} investigate in robust detail the UV continuum and
the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
adjacent continuum are covered by BOSS. These measurements provide
line profile information and flux ratios\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
their \civ properties in order to understand the high-$z$ ``Extremely
Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
  Zakamska2019}.  As such, we prefer the \citet{Hamann2017} emission line
values where available, though this is only for two out of our nine spectra.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Emission line evolution}
Emission line measurements from the catalogues of \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of
\citet{Calderone2017} are presented in Table~\ref{tab:
LineMeasurements}.

From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
there is some potential problem in using those data. However, visual
inspection shows strong broad \civ\ emission, so we disable the check on the mask,
and report the line fits in Table~\ref{tab:LineMeasurement}

@@

    \rowfont{\color{blue}}         &  56189     & \civ    &   32$\pm$3.5   &   7663$\pm$881       &    538$\pm$352       &   50.2$\pm$5.6      & ---                        &    QSFit  \\

@@

 \label{tab:LineMeasurements}

@@

%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
%% Using    C IV

@@

                              & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen11\\

@@

                              & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen11\\
    J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kozl17\\

@@

                              & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kozl17\\

@@

    M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\

@@

  \caption{Physical properties of the \civ\ CLQs and M87.
     $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
        bolometric corrections (BC = 3.81) in \citet{Richards2006b}.
        Virial BH masses using calibrations of \citet{VestergaardPeterson2006}.
         $\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio computed using the virial BH mass.

@@

        Kozl17 is \citet{Kozlowski2017}.
        EHT is \citet{EHT2019_PaperV}.      }

@@

\subsection{The \civ\ Baldwin Effect}
The Baldwin Effect (Baldwin 1977) is an empirical %inverse
relation between emission-line REWs and continuum luminosity in
quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}
%%
There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
so that as the underlying UV continuum luminosity increases, the EW decreses,
see Figure~\ref{fig:CIV_Baldwin}
Our Figure~\ref{fig:CIV_Baldwin} is a reproduction of Figure~15 from \citet{Calderone2017}.

The plotted values are \verb|CONT1450\_\_LUM| and \verb|BR\_CIV\_1549\_\_\EW|.
\verb|CONT1\_\_LUM| is the $\nu L_{\nu}$ luminosity at wavelength
%{\tt CONT1\_\_WAVE}, and the latter is always within the observed wavelength range, hence it is always present. We use the v1.2.4 of the QSFIT catalogue, applying the cuts: {\tt BR\_CIV\_1549\_\_LUM} $>0$ \&\& {\tt BR\_CIV\_1549\_\_EW} $>0$.
This selects 20,374 quasars.
%On the other hand, CONT1450__LUM is estimated at 1450AA (rest frame), hence it is available only if 1450AA is within the available
%wavelength range.  For SDSS data, CONT1450__LUM is available only if $z> 1.83$.

The slope $\beta$ is $-0.1997$. 
Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
in line with that from \citet{Hamann2017} ($\beta=-0.23$.

@@

%{\bf Our Eddington ratios \\
%Done 1\% \\
%Coatman, Hewett say \civ\ masses are okay.\\
%But what are these Eddington ratios? \\
%Low state BHs vs. High-mass BHs... \\
%Coatman et al?? Blue-shiftted \\ }
\section{Discussion}
The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

The Balmer series in hydrogen is due to the recombination cascade
between different principal quantum numbers $n$, and
the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$.

\civ\ is one of the strongest collisionally excited lines in quasar
spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
canonical BELR parameters deduced over from early analysis of the
\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
H$^{+}$).

\civ\ probes the photoionization environment produced by the innermost
disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
thin disk models, large changes in the continuum flux are not
permitted over short timescales due to the relatively long viscous
time associated with such disks. Given the observed short timescale
continuum variations, it is not surprising that the \citet{SS73} disk may fail
on other fronts. The \civ\ variations observed in our sources... 
%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}
\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.

@@

\begin{figure*}
  \centering
  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/MJD_vs_Eddington_20191104_v0pnt9.png}
  \vspace{-12pt}
  \caption[]{Eddington Ratios of the three \civ\ CLQs and M87.}
  \label{fig:Eddington_ratios}
\end{figure*}
\subsection{Eddington ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

The soft X-ray excess -- the excess of X-rays below 2 keV with respect
to the extrapolation of the hard X-ray spectral continuum model -- is
a very common feature among type 1 active galactic nuclei (AGN). 
\citet{NodaDone2018} note that
The soft X-ray excess produces most of the ionizing photons, so its
dramatic drop leads to the disappearance of the broad-line region,
driving the ``changing-look'' phenomena.  major difference is that
radiation pressure should be much more important in AGNs, so that the
sound speed is much faster than expected from the gas temperature.
%%
This spectral hardening appears similar to the soft-to-hard state
transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
an advection dominated accretion flow, while the overall drop in
luminosity appears consistent with the hydrogen ionization disc
instability.  Crucially \citet{NodaDone2018} make the prediction that
all changing-look AGNs are similarly associated with the state
transition at $L / L_{\rm Edd} \sim$a few per cent.
%%
\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
\citet{JiangYF2019arXiv} use global three dimensional radiation
magneto-hydrodynamic simulations to study the properties of inner
regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
black hole with mass accretion rates reaching 7\% and 20\% of the
Eddington value.

@@

%\subsection{Variability around billion solar mass black holes} 
The Event Horizon Telescope (EHT) mapped the central compact radio
source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI,
EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV,
EHT2019_PaperVI} .
